---
title: "Panel Data vs. Online Responses"
author: "Arielle Herman"
date: "6/16/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("../code/default_setup.R")
```

# Demographic Distribution in Panel Data vs. Online Responses

Below are bar plots that compare the demographic distributions of panel and online respondents in the following areas:

1. Gender
2. Race (census categories)
3. Marital Status
4. Religion
5. Sexual Orientation
6. Language Spoken at Home
7. Level of Education

The percents are calculated as the proportion of respondents in a given demographic category per respondent source.  For example, 57% of the panel respondents identified as female, whereas 78% of the online respondents identified as female.

```{r}
demographic_qs <- c("gen", "race_census", "mar", "relig", "sex", "not_eng", "sch_level")

plots <- lapply(demographic_qs, function(q) {
  sym_q <- sym(q)
  
  # hackey text fixes
  q_text <- survey_codebook_labelled$text[survey_codebook_labelled$full_name == q] %>%
    str_replace_all(c("(?<=completed).*" = "?", " \\(select one\\)" = ""))
  if(length(q_text) == 0) {
    q_text <- "Census Race Category"
  }
  
  plot <- wrangled %>%
    count(source = source == "eme", !!sym_q) %>%
    na.omit %>%
    group_by(source) %>%
    mutate(across(!!sym_q,
                  ~stringi::stri_trans_general(stringr::str_to_title(labelled::to_factor(.)),
                                               "latin-ascii")),
           prop = n / sum(n),
           # hackey text fixes
           across(!!sym_q, ~str_replace_all(., c("Transgender.*" = "Transgender",
                                                 "Indigenous.*" = "Indigenous American",
                                                 "^Yes$" = "Not English at Home",
                                                 "^No$" = "English at Home",
                                                 "^Married.*" = "Married / Partnership")))) %>%
    ggplot(aes(x = prop, y = reorder(!!sym_q, n), fill = source)) +
    geom_col(position = position_dodge(width = 0.9)) +
    geom_text(aes(label = glue::glue("{signif(prop, 2)*100}%"), color = source),
              hjust = -0.1, position = position_dodge(width = 0.9), size = 3.5, show.legend = FALSE) +
    
    scale_fill_manual(NULL, labels = c("Online Responses", "Panel (Emerson)"),
                      values = project_pal[c(1,3)]) +
    scale_color_manual(NULL, values = project_pal[c(1,3)]) +
    scale_x_continuous(labels = scales::percent, limits = c(0,1)) +
    ylab(NULL) + xlab(NULL) + ggtitle(str_to_sentence(q_text)) +
    theme(legend.position = "bottom") +
    labs(subtitle = "*Proportion of respondents by source")
  return(plot)
    #ggtitle(glue::glue("Income Distribution by {facet}"))
})
plots

```