---
title: "plan_of_analysis"
author: "Arielle Herman"
date: "2/11/2022"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
    df_print: paged
---

```{r setup, warning=F, message=F, include=F}
library(tidyverse)
library(haven)
library(gfonts)
library(ggVennDiagram)
source("default_setup.R")
```

# 1.2) People who are currently unemployed who were not unemployed in before the pandemic (March 2020)  [14&15]

```{r, include=F}
# 1.2.1 Run distribution over population
wrangled %>% count(emp_status_before) %>% mutate(time = "2020") %>% rename(emp_status_after = emp_status_before) %>%
  bind_rows(count(wrangled, emp_status_after) %>% mutate(time = "2021")) %>%
  group_by(time) %>% mutate(prop = round(n/sum(n), digits = 4)*100) %>%
  filter(emp_status_after %in% c("disabled", "employed", "unemployed", "retired")) %>%
  ggplot(aes(x = time, y = prop, color = emp_status_after, group = emp_status_after)) +
  geom_point(aes(size = prop)) + geom_line(show.legend = FALSE) +
  xlab(NULL) + ylab(NULL) + geom_vline(xintercept = 1.5, lty = "dashed") +
  scale_color_manual(values = project_pal)

# Run distribution by sub-demographics(a-k)
# two versions of the plots
dems_employment <- c(str_subset(demographics, "emp_status", negate = TRUE))
dems_employment <- setNames(dems_employment, dems_employment)

lapply(dems_employment, function(item) {
  sym_item <- sym(item)
  
  reshaped <- wrangled %>% count(dem = labelled::to_character(!!sym_item),
                            unemployed = emp_status_before== "unemployed") %>% mutate(time = "2020") %>%
    bind_rows(wrangled %>% count(dem = labelled::to_character(!!sym_item),
                            unemployed = emp_status_after == "unemployed") %>% mutate(time = "2021")) %>%
    group_by(time, dem) %>% mutate(denom = sum(n), prop = round(n/denom, digits = 4)) %>%
    filter(unemployed, !str_detect(dem, "prefer not"))
  
  plot <- reshaped %>% ggplot(aes(x = time, y = prop, color = dem, group = dem)) +
    geom_point(aes(size = denom), shape = 21) + geom_line(show.legend = FALSE) +
    scale_y_continuous(labels = scales::percent) +
    xlab(NULL) + ylab(NULL) + scale_color_discrete(guide = "legend", name = item) +
    ggtitle(glue::glue("Percent Newly Unemployed by {stringr::str_to_title(item)}")) + project_theme
  
  return(plot)

})

item <- "sch_level_cat"

min_exclude <- 10
```

The following plots indicate different demographics whose proportions of individuals who lost there jobs during the pandemic.  Categories with fewer than r`min_exclude` responses were excluded from the calculation.  The p-values are provided on the plots.

```{r}
plots <- make_plots(wrangled %>% mutate(emp_after_un_only = emp_after_un == 1, emp_before_un != 1),
           by_vars = dems_employment, hyp_var = "emp_after_un_only", min = 5)
length(filter(wrangled, !str_detect(emp_before, "unemp"), borough == "bronx")$unemployed == 1)
plots$not_eng <- plots$not_eng +
  ggtitle("Percent Newly Unemployed by\nwhether or not English is Spoken at Home") +
  scale_y_discrete(labels = c("English", "Not English"))
plots$hh_ch_0_17_bi <- plots$hh_ch_0_17_bi +
  ggtitle("Percent Newly Unemployed by Presence of Children at Home")
plots$inc_dist <- plots$inc_dist +
  ggtitle("Percent Newly Unemployed by Income Category")
#plots$res_cat <- plots$res_cat + ggtitle("Percent Newly Unemployed by Residence Category")
#plots$race_weight <- plots$race_weight + ggtitle("Percent Newly Unemployed by Race")
plots$borough
```


# 1.3) Higher income employees were less likely to face adverse job status changes during the pandemic

```{r}
make_plots(wrangled %>% filter(emp_change == 1), by_vars = "inc_be_med_before", hyp_var = "inc_neg")
```

# 1.5-1.6)

1.5) People with at least a Bachelor’s degree were more/less likely to face job status changes during the pandemic [11, 14,15]
1.6) People who had insurance (any form) were less likely to face changes in job status [21,14,15]

```{r}
#table(wrangled$ins[str_detect(wrangled$ins, ";")])
new_variables <- c("inc_be_med_before", "sch_bach", "ins_has", "ins_prvt")
new_variables <- setNames(new_variables, new_variables)

make_plots(df = wrangled,
           by_vars = new_variables,
           hyp_var = "emp_change", min = 5,
           title = "Proportion to Experience an Adverse job change")

make_plots(df = wrangled %>% filter(emp_change == 1),
           by_vars = new_variables,
           hyp_var = "inc_neg", min = 5,
           title = "Proportion to Experience an Adverse job change")
```

# 1.8, 1.13)

1.08) Higher paid employees (above median income) were less likely to return to working in-person [12,13,18]
1.13) Individuals with children were more likely to participate in hybrid work rather than full-time physical work
```{r}
# maybe we should make a variable that is all three categories (below, at above) or 
inc_1.8 <- c("inc_ab_med_before", "inc_be_med_before", "inc_dist", "hh_ch_0_17_bi")
names(inc_1.8) <- inc_1.8

make_plots(df = wrangled %>% mutate(wrk_vi = wrk %in% c(2,3)),
           by_vars = inc_1.8, hyp_var = "wrk_vi",
           title = "proportion who returned to work virtually or hybrid")
```

# 1.9-1.11)

1.09) People who are currently receiving unemployment benefits [16]
- only r`sum(wrangled$unemp_ben == 1, na.rm = TRUE)` people who are currently recieving unemployment benefits

1.10) People who are unemployed and are not receiving unemployment benefits because they expired [15 &16]

```{r}
dems_unemp <- str_subset(demographics, "un|emp", negate = TRUE)
dems_unemp <- setNames(dems_unemp, dems_unemp)

wrangled %>% count(unemp_ben) %>% mutate(label = labelled::to_factor(unemp_ben))

lapply(c(2, 4), function(label) {
  title <- names(attributes(wrangled$unemp_ben)$labels[label])
  mutated <- wrangled %>% mutate(unemp = unemp_ben == label)
  make_plots(mutated, dems_unemp, "unemp", title = title)
})
```

# 1.12) Unemployed people who have less than a bachelors degree are more or less likely to apply for unemployment benefits even if they qualify [11, 15,16]


```{r}
wrangled$unemp_ben
make_plots(wrangled %>% filter(emp_before_un == 1) %>% mutate(sch_bach_bi = sch_bach == "BA plus",
                                                              unemp_ben_app = unemp_ben !=4 ), "sch_bach_bi", "unemp_ben_app")
```

# validation

```{r}
wrangled %>% filter(str_detect(emp_after, "unemployed;|;unemployed")) %>%
  select(responseid, source, wrk, emp_after, emp_before) %>% mutate_if(labelled::is.labelled, labelled::to_character)

wrangled %>% count(wrk, emp_after) %>%
  filter(wrk == 4) %>%
  mutate_if(labelled::is.labelled, labelled::to_character)

filter(wrangled, wrk == 4, str_detect(emp_after, "full|part")) %>% select(responseid, source, wrk, emp_after, emp_before) %>%
  mutate_if(labelled::is.labelled, labelled::to_character)

filter(wrangled, wrk == 3, str_detect(emp_after, "unemp|dis")) %>% select(responseid, source, wrk, emp_after, emp_before) %>%
  mutate_if(labelled::is.labelled, labelled::to_character)

# everybody who started unemployed was still unemployed
wrangled %>% filter(!str_detect(emp_after, "un"), str_detect(emp_before, "un"), !is.na(unemp_ben)) %>% select(responseid, emp_before, emp_after, unemp_ben) %>%
  mutate_if(labelled::is.labelled, labelled::to_character)

# people who lost their jobs and did not get new ones
wrangled %>% filter(str_detect(emp_after, "un"), !str_detect(emp_before, "un"), !is.na(unemp_ben)) %>% select(responseid, emp_before, emp_after, unemp_ben) %>%
  mutate_if(labelled::is.labelled, labelled::to_character)

```

# 1.1

```{r include=F, eval=F}
lapply(demographics, function(dem) {
  sym_dem <- sym(dem)
  reshape <- wrangled %>% count(emp_change, !!sym_dem) %>% na.omit()
  
  if(is.character(reshape[[dem]])) {
    reshaped <- reshape %>% arrange(n) %>% mutate_at(vars(!!sym_dem), stringr::str_to_title)
  } else if(haven::is.labelled(reshape[[dem]])){
    reshaped <- reshape %>% arrange(!!sym_dem) %>%
      mutate_at(vars(!!sym_dem), ~stringr::str_to_title(haven::as_factor(.)))
  } else if (dem == "age") {
    reshaped <- reshape %>% mutate_at(vars(!!sym_dem), ~as.factor(floor(./10)*10)) %>%
      group_by(emp_change, !!sym_dem) %>% summarize(n = sum(n))
  } else {
    reshaped <- reshape %>%
      mutate_at(vars(!!sym_dem), ~stringr::str_to_title(as.factor(.))) %>% arrange(n)
      
  } 
  p <- reshaped %>% group_by(!!sym_dem) %>% mutate(prop = n/sum(n)) %>%
    filter(emp_change) %>%
    ggplot(aes(x = prop, y = !!sym_dem, fill = emp_change, alpha = n,
               show.legend = FALSE)) +
    geom_col() + xlab(NULL) + ylab(NULL) +
    scale_fill_manual(labels = rev(c(FALSE, TRUE)), values = project_pal) +
    #scale_x_reverse()
    theme(legend.position = "none")
  return(p)
})
# does not yet fix for double counting
wrangled %>%
  group_by(responseid, emp_change = emp_before != emp_after) %>%
  select(responseid, contains("race_"), -race_text, -race_twomore) %>%
  pivot_longer(cols = c("race_white", "race_black", "race_his_lat"),
               names_to = "category", values_to = "value") %>%
  filter(value != 0) %>% ungroup %>% count(category, emp_change) %>%
  ggplot(aes(x = n, y = category, fill = emp_change, alpha = n)) + geom_col(position = "fill") +
  scale_fill_manual(labels = rev(c(FALSE, TRUE)), values = c(project_pal[1], "white")) + scale_x_reverse()


race_df <- wrangled %>% select(responseid, race_white, race_black, race_his_lat) %>%
  pivot_longer(cols = c(race_white, race_black, race_his_lat), names_to = "cat", values_to = "value") %>%
  filter(value == 1)

race_list <- split(race_df$responseid, race_df$cat)

ggVennDiagram(race_list)

mean(wrangled$emp_after_dis)
mean(wrangled$emp_before_dis)
```

# ester's table
```{r}
wrangled %>% filter(hh_ch_0_17_bi == 1) %>% count(race_census, diff_cc) %>% drop_na %>% group_by(race_weight) %>% mutate(prop = n/sum(n)) %>%
  filter(diff_cc == 1)
wrangled %>% filter(hh_ch_0_17_bi == 1) %>% group_by(race_weight) %>% summarize(prop = mean(need_cc, na.rm = TRUE)) %>%
  mutate(type = "Difficulty affording childcare") %>%
  bind_rows(wrangled %>% filter(hh_ch_0_17_bi == 1) %>%
              group_by(race_weight) %>% summarize(prop = mean(diff_cc, na.rm = TRUE)) %>%
              mutate(type = "Difficulty finding or relying on childcare")) %>%
  drop_na %>% filter(!str_detect(race_weight, "two|american")) %>%
  pivot_wider(id_cols = type, names_from = race_weight, values_from = prop) %>%
  mutate_if(is.double, ~glue::glue("{signif(., digits = 2)*100}%"))

wrangled %>% filter(hh_ch_0_17_bi == 1) %>% select(diff_cc, need_cc) %>% summarize_all(~glue::glue("{signif(mean(., na.rm = TRUE), 2)*100}%"))

filter(wrangled, hh_ch_0_17_bi == 1, race_weight == "asian", diff_cc == 1) %>% nrow


wrangled %>% filter(hh_ch_0_17_bi == 1) %>%
  group_by(race_weight) %>%
  summarize_at(vars(diff_worr, diff_ran_out, diff_bill, diff_rent),
                   ~mean(., na.rm = TRUE)) %>% #filter(diff_worr > .25) %>%
  left_join(
    wrangled %>% group_by(hh_ch_0_17_bi) %>%
    summarize_at(vars(diff_worr, diff_ran_out, diff_bill, diff_rent),
                   ~mean(., na.rm = TRUE)) %>%
      mutate_at(vars(hh_ch_0_17_bi), labelled::to_character)) %>%
  mutate_if(is.double, ~glue::glue("{signif(., digits = 2)*100}%")) %>%
  select(`household without children`, `household with children`, `black or african american`, `hispanic or latinx`, asian, `white (non-hispanic or latino)`)

wrangled %>% filter(hh_ch_0_17_bi == 1, race == "asian") %>% pull(diff_ran_out) %>% table(useNA = c("ifany"))
  count(diff_worr) %>% ungroup

wrangled %>% filter(hh_ch_0_17_bi == 1) %>% pull(att_sch_in_prsn) %>% mean(na.rm = TRUE)
wrangled %>% filter(hh_ch_0_17_bi == 1) %>% pull(con_covid) %>% mean(na.rm = TRUE)
wrangled %>% filter(hh_ch_0_17_bi == 1) %>% group_by(borough) %>% summarize(prop = mean(con_covid, na.rm = TRUE))
wrangled %>% filter(hh_ch_0_17_bi == 1) %>% group_by(race_weight) %>% summarize(prop = mean(con_covid, na.rm = TRUE))
wrangled %>% group_by(hh_ch_0_17_bi) %>% summarize(prop = mean(boost %in% c(1,2), na.rm = TRUE))
wrangled %>% filter(hh_ch_0_17_bi == 1) %>% group_by(borough) %>% summarize(prop = mean(find_cc == 0, na.rm = TRUE))
wrangled %>% filter(hh_ch_0_17_bi == 1) %>% group_by(race_weight) %>% summarize(prop = mean(need_cc, na.rm = TRUE))

# question: proportion of people who drop by demographics is the same as the people who stay in
# boostrapping (sample with replacement of the same size, what is the minimum sample size)
```

```{r eval=F}

ggsave(plots$borough, filename = "../visuals/unemployment_borough.png")
drive_upload(media = "../visuals/unemployment_borough.png",
             path = "Communities Speak/Subteams/Data Subteam/Data Findings + VIZ_IS_2/Viz/unemployment_borough0328.png",
             overwrite = TRUE)
ggsave(p_adverse, filename = "../visuals/adverse_employment_income.png")
drive_upload(media = "../visuals/adverse_employment_income.png",
             path = "Communities Speak/Subteams/Data Subteam/Data Findings + VIZ_IS_2/Viz/adverse_employment_income0328.png",
             overwrite = TRUE)

drive_upload(media = "plan_of_analysis.pdf", path = paste0("Communities Speak/Subteams/Data Subteam/Data Findings + VIZ_IS_2/Findings/POA_PARTIAL_ARIELLE_0326.pdf"))
```
