---
title: "poa_safety"
author: "Arielle Herman"
date: "4/9/2022"
output: pdf_document
---

```{r setup, include=FALSE}
source("default_setup.R")
```

# Summary

Felt unsafe appears to be capturing the opposite of worried about discrimination

# 5.1)People who experienced or worried about discrimination due to the pandemic [30]

Run distribution over population
Run distribution by sub-demographics (a-k)
Compare and find gaps (test unequal proportions)

```{r}
mean_val = mean(wrangled$discrim_bi, na.rm = TRUE)
make_plots(wrangled, demographics, "discrim_bi", title = "Percent Respondents who experienced or\nworried about discrimination due to the pandemic")
```

5.2)People who felt unsafe in their neighborhood in the past six months [17]
Run distribution over population
Run distribution by sub-demographics (a-m)
Compare and find gaps (test unequal proportions)
5.3)Respondents who have a low income (below median income) are more likely to experience  violence ]12 &13]
Find proportion who faced discrimination or violence[34]
Find subset who are below median income[13]
Compare and contrast with group who are above median income within the larger proportion

```{r}
mean(wrangled$diff_neigh, na.rm = TRUE)

make_plots(wrangled, demographics, "diff_neigh", title = "Percent Respondents Who Felt Unsafe in their neighborhood")
```

# 5.4)Respondents who are homemakers are more likely to experience verbal abuse and physical violence since the pandemic started [14, 15, 34, 35]

Find proportion of respondents who faced discrimination or violence when homemakers before [14] compared to after [15] the pandemic
Compare proportion of respondents who experienced violence and were homemakers before but not after, with those who were homemakers after but not before
Compare homemakers to nonhomemakers
Run on subdemographics (a-m)

```{r}
wrangled %>% count(emp_before_hm, emp_after_hm, exp_ab_and_vi)
```

# 5.5)Respondents in the gig economy are more worried about safety, from covid-19 [26a, 41]

Find proportion of respondents who were in the gig economy and those who are not
FInd subset who are worried about covid-19 generally [26a] or about delta variants [41]
Compare proportion who are gig economy with those who are not

```{r}
wrangled %>% count(emp_before_gig, emp_after_gig, vrnts_bi)
make_plots(wrangled, "emp_before_gig", "vrnts_bi")
```

# 5.6)Respondents who felt unsafe in their neighborhoods were dissatisfied with other community services [32]

Find proportion of respondents who felt unsafe in their neighborhood [17]
Run binary distribution of who did and did not feel unsafe over the following categories from question 32:
Emergency medical services
Maintenance of parks and recreational facilities
Police responsiveness to calls or complaints
Prevents of local crime / safety
Group respondents by whether or not they were dissatisfied with one of the above four listed neighborhood services
Compare those who did and did not feel unsafe

```{r}
q34 <- c("rate_neigh_med", "rate_neigh_rec", "rate_neigh_pol", "rate_neigh_pre")
make_plots(wrangled %>% mutate(across(q34, ~.>3)), q34, "diff_neigh",
           title = "Proportion of Respondents who\nFelt Unsafe by Dissatisfaction with...")
```

# 5.7)Respondents who are dissatisfied with housing code enforcement are more likely to feel unsafe in their neighborhood[32, 17]

Find proportion who felt unsafe in neighborhood
Find subset who are dissatisfied with housing code enforcement
Compare proportion who did and did not feel unsafe depending on dissatisfaction with housing code enforcement

```{r}
make_plots(wrangled %>% mutate(rate_neigh_code_bad = rate_neigh_code > 3), "diff_neigh", "rate_neigh_code_bad")
```

# 5.8)Respondents of certain races are more likely to experience abuse / violence / discrimination [34, 35]

Run binary distribution by race

```{r}
make_plots(wrangled, "race_census", "exp_ab_or_vi", title = "Percent Respondents who Experienced\nViolence or Abuse due to COVID-19")
```

