---
title: "poa_access_gov"
author: "Arielle Herman"
date: "4/10/2022"
output: pdf_document
---

```{r setup, include=FALSE}
source("default_setup.R")
```


# 7.1)People who had difficulty accessing social services or benefits [20]

Run distribution over population
Run distribution by sub-demographics (a-k)
Compare and find gaps (test unequal proportions)

```{r}
mean(wrangled$diff_ss, na.rm = TRUE)

make_plots(wrangled, demographics, "diff_ss", title = "Difficulty accessing Social security benefits")
```

# 7.2)People who are hesitant to use public transport facilities[40]
                1. Run distribution over population
                2.  Run distribution by sub-demographics (a-k)
                                        a. Compare and find gaps (test unequal proportions)
                                        
```{r}
mean(wrangled$hstnt_trans, na.rm = TRUE)

make_plots(wrangled, demographics, "hstnt_trans", title = "Hesitant to Use public transit")
```

# 7.3)Households with children in public schools are more likely to give higher ratings to neighbourhood public schools [32, 24]

Run binary distribution for overall rating of neighbourhood schools 
Not Poor=Excellent, Good
Poor=Fair, Poor
Find subset of population which are hhs with children in each binary category 
Compare the strength of the subset with non-hhs with children in each subset

```{r}
mean(wrangled$rate_neigh_pub, na.rm = TRUE)
mean(wrangled$rate_neigh_pub_good, na.rm = TRUE)
mean(wrangled$rate_neigh_pub_bad, na.rm = TRUE)


make_plots(wrangled, "hh_ch_0_17_bi", "rate_neigh_pub_good", title = "Good or Excellent Rating of Public Schools")
make_plots(wrangled, "hh_ch_0_17_bi", "rate_neigh_pub_bad", title = "Poor or Very Poor Rating of Public Schools")
```

# 7.4)Attitude towards Police Responsiveness

Run binary distribution over the overall rating of Police responsiveness (as described in 7.3)
Run distribution by sub-demographics

```{r}
mean(wrangled$rate_neigh_pol, na.rm = TRUE)
mean(wrangled$rate_neigh_pol_good, na.rm = TRUE)
mean(wrangled$rate_neigh_pol_bad, na.rm = TRUE)

make_plots(wrangled, demographics, "rate_neigh_pol_good", title = "Positively Rated Police Responsiveness")
make_plots(wrangled, demographics, "rate_neigh_pol_bad", title = "Negatively Rated Police Responsiveness")
```


# 7.6)Respondents from the Bronx (high crime rate as compared to to other boroughs) are more likely to rate Police Responsiveness as poor [32, 2]

Run binary distribution for overall rating of Police responsiveness (as described in 7.3)
Find subset of population who are from Bronx in both the category responsenses
Compare and contrast the responses between the Bronx and on-Bronx population

```{r}
make_plots(wrangled, "borough", "rate_neigh_pol_bad", "Negatively Rated Police Responsiveness")
```

# 7.7)Respondents from low income brackets (below median income) are more likely to rate neighbourhood safety poorly

Run binary distribution for overall rating of Police responsiveness (as described in 7.3)
Find subset of population who are from above median income  in both the category responsenses
Compare and contrast the responses between high and low income population

```{r}
mean(wrangled$rate_neigh_pre_bad, na.rm = TRUE)
make_plots(wrangled, "inc_dist", "rate_neigh_pre_bad", title = "Rated Crime Prevention Well")
make_plots(wrangled, "inc_dist", "rate_neigh_pre_good", title = "Rated Crime Prevention Poorly")

make_plots(wrangled, "borough", "lr_gov")
make_plots(wrangled, "borough", "lr_fam")
```


# 7.8) People who rated city/state/federal government response to the pandemic well were more likely to indicate they would turn to the government if they needed help

Find respondents who rated city/state/federal government response as good or excellent [33]
Find proportion of subset who indicated they would use the government for at least one need [34]
Find proportion not in subset who indicated they would use the government for at least one need and compare (test unequal proportions)

```{r}
prop_rate_above_ave <- mean(wrangled$rate_gov_good, na.rm = TRUE)

mean_val <- mean(6 - wrangled %>% select(rate_gov_fed, rate_gov_sta, rate_gov_cit) %>% unlist, na.rm = TRUE)

wrangled %>% ggplot(aes(x = rate_gov_ave)) + geom_bar() + geom_vline(xintercept = mean_val)

make_plots(wrangled, "lr_gov", "rate_gov_bad", title = "Rated Federal, State, and City Government (Very) poorly")
make_plots(wrangled, "lr_gov", "rate_gov_good")
```
# cell 13

Which populations are most and least likely to turn to the government for resources? By borough, race, booster status, socioeconomic status (below pov, below median, above median), mental health status (those who experienced one or more vs those who experienced none, families with children vs without

Also run these same demographics by who is most likely to turn to faith-based institutions, community-based organizations, and friends and family

```{r}
demo_plus <- c(demographics, "boost_bi", "mntl_hlth_bi", "mntl_hlth_state_bi")
names(demo_plus) <- demo_plus

make_plots(wrangled, demo_plus, "lr_gov", title = "Percent Respondents Who\nwould reach out to the Government")[c("borough", "race_census", "sch_level_cat", "inc_dist")]

make_plots(wrangled, demo_plus, "lr_fam", title = "Percent Respondents Who\nwould reach out to Friends and Family")[c("borough", "race_census", "sch_level_cat", "hh_ch_0_17_bi", "inc_dist", "emp_status_after", "res_cat", "mntl_hlth_bi")]


make_plots(wrangled, demo_plus, "lr_fb", title = "Percent Respondents Who\nwould reach out to faith-based organizations")

make_plots(wrangled, demo_plus, "lr_np", title = "Percent Respondents Who\nwould reach out to local nonprofits")


issues <- c("stress", "food", "wtr", "hc")
resources <- c("fam", "gov", "fb", "np")
variables <- lapply(issues, function(issue) paste("lr", issue, resources, sep = "_")) %>% unlist
names(variables) <- variables
lapply(variables[1:2], function(variable) {
  splitted <- stringr::str_split(variable, "_") %>% unlist
  issue <- splitted[2]
  resource <- splitted[3]
  make_plots(
    wrangled, demo_plus, variable,
    title = glue::glue("Percent Respondents who would reach out to\n{resource} regarding {issue}"))
})


```

# cell 14

Run government ranking over other health indicators (i.e. what percent of those who experienced at least one mental health challenge rated the gov below average vs the percent that rated the gov below average that did not experience mental health challenge at all levels of gov)

Other health indicators: access to health insurance, personally experienced covid, experienced covid in the household, and ran out or worried about running out of food (combined)

```{r}
health_indicators <- c("mntl_hlth_state_bi", "mntl_hlth_bi", "ins_has", "posi_yes", "posi_hh", "posi", "food_insec")
names(health_indicators) <- health_indicators
attributes(wrangled$food_insec)$labels
make_plots(wrangled, health_indicators, "rate_gov_bad",
           title = "Percent Respondents Who\nRated the government below average")
```

# cell 15

"Look at the government ratings (all levels of gov) for those who rated a neighborhood service as ""fair"" or poor"" vs the gov ratings of those who rated that same service as ""Excellent"" or ""good""

Run for all neighborhood services "

```{r}
neighbor_services <- wrangled %>% select(contains("rate_neigh") & !contains("good") & !contains("bad")) %>% colnames()
attributes(wrangled$rate_gov_good)$labels
make_plots(wrangled, neighbor_services, "rate_gov_good", title = "rated government positively")
```